Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals

### 2025-03-12 template.tex
Big update: plotting results, finished envelope math

\sigma_{\rm t} \sigma_{\rm f} \geq \frac{1}{2\pi}

@@

\item Equation \ref{eq:awesome} will now be applied, using the definition of $r_a(t)$ and the Fourier transform of $s(t)$, $S(f)$.  The Fourier transform of $r_a(t) * s_a(t)$ is $R_a(f) S_a(f)$.  Using the definition of the analytic signal, we have

@@

R_a(f) S_a(f) = R_a(f)(1 + \sgn(f)) S(f) \label{eq:midway}

@@

The Fourier transform of $r_a(t)$ is

@@

R_a(f) &= \frac{R_0}{2\pi j} \frac{1}{f-z_0} \\
z_0 &= f_0 + \frac{j\gamma}{2\pi}

@@

The Fourier transform $S(f)$ is given by Eq. \ref{eq:spec}.  Inserting the spectra into Eq. \ref{eq:midway} and taking the inverse Fourier transform should give $r_a(t) * s_a(t)$.  Note the inverse transform integral is only over positive frequencies, due to the $1+\sgn(f)$ factor.  Introducing the time derivative removes a factor of $(2\pi j f)$ from the numerator of the integrand.  Note also that it is prudent to consider the signal $s(t)$ shifted by a $t_0$, to ensure the entire signal is convolved with $r(t)$.  For time-shifts, the Fourier transform responds like:
\mathcal{F}\left\lbrace s(t-t_0)\right\rbrace = e^{-2\pi f t_0} S(f)
The result is

@@

r_a(t) * s_a(t) = \\ -j \sqrt{\frac{2}{\pi}} R_0 E_0 \sigma_t^3 \frac{d}{dt} \int_0^\infty \frac{e^{2\pi j f(t-t_0)} e^{-\frac{1}{2}\left(\frac{f}{\sigma_f}\right)^2}}{f-z}df

@@

Completing the square in the exponent, and letting $x = (t-t_0)/(\sqrt{2}\sigma_t)$, $y = f/(\sqrt{2}\sigma_f)$, and $z_0 \to f_0/(\sqrt{2}\sigma_f)+j \gamma/(2\pi\sqrt{2}\sigma_f)$, we find

@@

r_a(t) * s_a(t) = \\ -\frac{j}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \frac{d}{dx} \left(e^{-x^2} \int_0^{\infty} \frac{e^{(x+jy)^2}}{y-z_0} dy \right) \label{eq:withI}

@@

All that remains is to evaluate the integral
I(z,z_0) = \int_0^{\infty} \frac{e^{(x+jy)^2}}{y-z_0} dy
Let $z = x+jy$, $dy = -jdz$, and $z_1 = x+jz_0$.  The integral becomes, as $R \to \infty$,
I(x,z_0) = \int_{x}^{x+jR} \frac{e^{z^2}}{z - z_1} dz
$I(x,z_0)$ can be evaluated via contour integration, with a rectangular contour that encloses the pole if $x > \Im\lbrace z_0\rbrace$.  Let $I_1$ extend from $(x,0)$ to ($x,jR)$.  Let $I_2$ extend from $(x,jR)$ to $(0,jR)$.  Let $I_3$ extend from $(0,jR)$ to $(0,0)$.  Finally, let $I_4$ extend from $(0,0)$ to $(x,0)$.  Note that $I_1 = I(x,z_0)$.  For the integral $I_2$, note that the exponential factor is proportional to $\exp(-R^2)$, while the denominator contains another factor of $R$.  Since $dz = dx$, the integrand goes as $\exp(-R^2)/R$, vanishing as $R \to \infty$.  For $I_3$, $x=0$.  Thus, it reduces to
I_3 = - \int_{0}^{R} \frac{e^{-y^2}}{y-z_0} dy = -G(-z_0) = G(z_0)

The function $G(z_0)$ is a function with odd-symmetry known as the Goodwin-Staton integral.  $G(z_0)$ appears in radiation transport, neutron transport, and optical calculations.  It is commonly used in problems involving diffusion approximations, particularly in media with semi-infinite boundary conditions. The final segment of the contour is
\begin{equation}
I_4 = \frac{j}{z_0}\int_{0}^{x} e^{x'^2} dx'
\end{equation}
The sum of contour segments is $I_1 + I_2 + I_3 + I_4 = I_{\rm C}$, where $I_{\rm C}$ is given by the Cauchy integral formula: $2\pi j e^{z_1^2}$.  Solving for $I(x,z_0)$, we find
\begin{equation}
I(x,z_0) = 2\pi j e^{z_1^2} - G(z_0) - \frac{j}{z_0}\int_{0}^{x} e^{x'^2} dx'
\end{equation}
If $x < \Im\lbrace z_0\rbrace$,
\begin{equation}
I(x,z_0) = -G(z_0) - \frac{j}{z_0}\int_{0}^{x} e^{x'^2} dx'
\end{equation} \\
Inserting this result into Eq. \ref{eq:withI},
\begin{multline}
r_a(t) * s_a(t) = \\ -\frac{j}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \left(\frac{dA(x,z_0)}{dx}-\frac{j}{z_0}\frac{dD(x)}{dx} \right) \label{eq:ra_sa_1}
\end{multline}
with
\begin{align}
A(x,z_0) &= 2\pi j e^{z_1^2} e^{-x^2} - G(z_0)e^{-x^2}, ~~ x > \Im \lbrace z_0 \rbrace\\
A(x,z_0) &= -G(z_0)e^{-x^2}, ~~ x < \Im \lbrace z_0 \rbrace
\end{align}
and
\begin{equation}
D(x) = e^{-x^2} \int_{0}^{x} e^{x'^2} dx'
\end{equation}
What remains is to compute the magnitude of Eq. \ref{eq:ra_sa_1}.  Let the overall scale factor in Eq. \ref{eq:ra_sa_1} be $R_0 E_0 \sigma_t^2/\sqrt{\pi}$, let $z_0 = x_0 + j y_0$, $\phi_0 = \tan^{-1}(y_0/x_0)$, and let $x>\Im\lbrace z_0\rbrace$.  Upon taking the magnitude, the quantity in parentheses generates four terms.  The first is
\begin{multline}
\left(\frac{dA}{dx}\right)^{*}\left(\frac{dA}{dx}\right) = \\ 16\pi^2|z_0|^2 e^{-4x y_0 - 2(x_0^2-y_0^2)} \\ + 4G^2(z_0)x^2 e^{-2x^2} \\ - 16\pi G(z_0) x e^{-x^2}e^{-2xy_0} e^{-x_0^2+y_0^2} \\ \times \left(|z_0|\cos(2x_0(x-y_0)+\phi_0) \right)
\end{multline}
The second is
\begin{equation}
\frac{1}{|z_0|^2}\left(\frac{dD(x)}{dx}\right)^2 = \frac{1}{|z_0|^2}\left(1-4xD(x)+4x^2D^2(x) \right)
\end{equation}
The combination of the third and forth terms is
\begin{multline}
j\frac{dD}{dx}\left\lbrace \frac{1}{z_0^{*}} \left(\frac{dA}{dx}\right) - \frac{1}{z_0} \left(\frac{dA}{dx}\right)^{*}\right\rbrace = \\
\end{multline}
\end{itemize}

>>>>

\sigma_t \sigma_f \geq \frac{1}{2\pi}

@@

\item The goal is now to apply Eq. \ref{eq:awesome} by convolving $s_a(t)$ with $r_a(t)$.  The real part of $s_a(t)$ can be convolved with $r_a(t)$ in the time domain.  As in Eq. \ref{eq:sa_4}, real part of $s_a(t)$ is $s(t)$.  Since $r_a(t<0)=0$, the convolution is written

@@

r_a(t) * \Re\lbrace s_a(t) \rbrace = \int_0^{\infty} r(\tau) s(t-\tau) d\tau

@@

Let $x=t/(\sqrt{2}\sigma_t)$, $y=\tau/(\sqrt{2}\sigma_t)$, and $z_0 = \sqrt{2}\sigma_t(\gamma-2\pi jf_0)$. The convolution may be organized as follows
r_a(t) * \Re\lbrace s_a(t) \rbrace = R_0 s(t) I + R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t^2)} \frac{dI}{dt} \label{eq:conv}
with
I(x,z_0) = \sqrt{2}\sigma_t \int_0^{\infty} e^{-y^2 + (2x-z_0)y} dy
Let $b = x-z_0/2$. Completing the square in the exponent produces
I(x,z_0) = \sqrt{2}\sigma_t e^{b^2} \int_0^{\infty} e^{-(y-b)^2} dy
The integral may be cast as a complementary error function by substituting $u=y-b$ and letting $b=jz$:
I(x,z_0) = \sqrt{\frac{\pi}{2}}\sigma_t e^{-z^2}\erfc(-jz)
Thus, the integral is proportional to the \textit{Faddeeva function}, $w(z)$:
I(x,z_0) = \sqrt{\frac{\pi}{2}} \sigma_t w(z) \label{eq:fadd}
Subsituting Eq. \ref{eq:fadd} into Eq. \ref{eq:conv}, and simplifying, produces
r_a(t) * \Re\lbrace s_a(t) \rbrace = \sqrt{\frac{\pi}{2}}R_0 \sigma_t s(t) w(z) \\
-j\frac{\sqrt{\pi}}{2} R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t)^2} \frac{dw(z)}{dz}
Turning to the convolution of $r_a(t)$ with $\Im(s_a)$, note that the imaginary part of Eq. \ref{eq:sa_4} contains $dD(x)/dx$, the derivative of the Dawson function.  To complete the convolution, the inverse Fourier transform of the product of the Fourier transforms of $r_a(t)$ and $\Im\lbrace s_a(t)\rbrace$ is calculated.  To complete this step, the Fourier transform of $dD(x)/dx$ is needed:

@@

x &= t/(\sqrt{2}\sigma_t) \\
f' &= \sqrt{2} \sigma_t f \\
\mathcal{F}\left\lbrace \frac{dD(x)}{dx}\right\rbrace &= \int_{-\infty}^{\infty} \frac{dD(x)}{dx}e^{-2\pi jft} dt \\
\mathcal{F}\left\lbrace \frac{dD(x)}{dx}\right\rbrace &= \sqrt{2}\sigma_t(2\pi jf') \int_{-\infty}^{\infty} D(x) e^{-2\pi jf'x} dx \\
\mathcal{F}\left\lbrace \frac{dD(x)}{dx}\right\rbrace &= 2\pi^2 \sigma_t^2 f e^{-\frac{1}{2}(f/\sigma_f)^2} \sgn(f)

@@

Let $z_0 = (\gamma - 2\pi jf_0)$, so that the Fourier transform of $r_a$ is 
\mathcal{F}\left\lbrace r_a(t)\right\rbrace &= R_0\int_{-\infty}^{\infty} e^{-zt} e^{-2\pi j ft} dt \\
\mathcal{F}\left\lbrace r_a(t)\right\rbrace &= \frac{R_0}{z_0+2\pi j f}
Let $z_1 = f_0 + j\gamma/(2\pi)$. Multiplying the Fourier transforms, and simplifying, yields

@@

\mathcal{F}\left\lbrace r_a(t) * \Im\left\lbrace s_a(t)\right\rbrace \right\rbrace = \\ -j \sqrt{2\pi} R_0 E_0 \sigma^3 \frac{f\sgn(f) e^{-\frac{1}{2}(f/\sigma_f)^2}}{f-z_1}

@@

The inverse Fourier transform now gives $r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace$:

@@

r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
-j\sqrt{2\pi} R_0 E_0 \sigma_t^3 \int_{-\infty}^{\infty} \frac{f\sgn(f)e^{-\frac{1}{2}(f/\sigma_f)^2}e^{2\pi jft}}{f-z_1} df

@@

Let $y = f/(\sqrt{2}\sigma_f)$, $x=t/(\sqrt{2}\sigma_t)$, $\sgn(f) = \sgn(y)$, and $z_1 \to f_0/(\sqrt{2}\sigma_f) + j\gamma/(2\pi \sqrt{2} \sigma_f)$.  The inverse Fourier transform can be organized as:
r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
-\frac{R_0E_0\sigma_t^3}{\sqrt{2\pi}}\frac{d}{dt}\int_{-\infty}^{\infty} \frac{\sgn(y) e^{-y^2+2jxy}}{y-z_1} dy
Completing the square in the exponent, factoring a unit of $j$ from the exponent, and changing the derivative from $d/dt$ to $d/dx$ gives
r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
-\frac{R_0E_0\sigma_t^2}{2\sqrt{\pi}}\frac{d}{dx}e^{-x^2} \int_{-\infty}^{\infty} \frac{\sgn(y) e^{(x+jy)^2}}{y-z_1}
\end{itemize}
